---
output: github_document
bibliography: vignettes/resources/references.json
link-citations: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# daedalus.compare: Run Multiple DAEDALUS Scenarios of Pandemic Outcomes

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
[![R build status](https://github.com/jameel-institute/daedalus.compare/workflows/R-CMD-check/badge.svg)](https://github.com/jameel-institute/daedalus.compare/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jameel-institute/daedalus.compare/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jameel-institute/daedalus.compare?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/daedalus.compare)](https://CRAN.R-project.org/package=daedalus.compare)
<!-- badges: end -->

_daedalus.compare_ is a helper package that wraps the _daedalus_ package for epi-macroeconomic modelling, and is primarily focused on making it easy to run multiple scenarios of pandemic mitigation strategies along with uncertainty in infection parameters.

## Installation

You can install the development version of _daedalus.compare_ from the Jameel Institute R-universe (recommended) or from GitHub.
 
```r
# installation from R-universe
install.packages(
  "daedalus.compare", 
  repos = c(
    "https://jameel-institute.r-universe.dev", "https://cloud.r-project.org"
  )
)

# installation from GitHub using {pak}
install.packages("pak")
pak::pak("jameel-institute/daedalus.compare")
```

You can also install 

## Quick start

This example shows how to model multiple pandemic response scenarios in the U.K. with uncertainty in $R_0$ of an H1N1-like infection.
**Note that** _daedalus.compare_ only supports running `daedalus::daedalus_multi_infection()` using `daedalus.compare::run_scenarios()` at present.

```{r}
library(daedalus)
library(daedalus.compare)

# make list of infection objects with R0 of 1.0 -- 2.0 with skewed distribution
set.seed(1) # for reproducible results
infection_list <- make_infection_samples(
  "influenza_2009",
  param_distributions = list(
    r0 = distributional::dist_beta(2, 5)
  ),
  param_ranges = list(
    r0 = c(1.0, 2.0)
  ),
  samples = 10
)

elimination <- daedalus_timed_npi(
  start_time = 10,
  end_time = 100,
  openness = list(
    daedalus.data::closure_strategy_data[["elimination"]]
  ), # must be a list
  "GBR" # must specify country
)

# run multiple scenarios of outputs
output <- run_scenarios(
  "GBR", infection_list,
  response = list(
    none = NULL,
    elimination = elimination
  ),
  time_end = 200
)

# view output which is a data.table
output

# get epi-curve data
disease_tags <- sprintf("sample_%i", seq_along(infection_list))
epi_curves <- get_epicurve_data(output, disease_tags)
```

```{r}
# plot epi-curve data showing daily hospitalisations
library(dplyr)
library(ggplot2)

epi_curves %>%
  filter(measure == "daily_hospitalisations") %>%
  ggplot(aes(time, value)) +
  geom_line(
    aes(col = response, group = interaction(tag, response))
  ) +
  labs(
    x = "Time", y = "Daily hospitalisations",
    col = "Mitigation strategy"
  )
```

## Related projects

_daedalus.compare_ is intended to be a helper package for the macro-economic and epidemiological [modelling package _daedalus_](https://github.com/jameel-institute/daedalus), also developed at the Jameel Institute.

The DAEDALUS model was originally developed in @haw2022, and the R implementation of the model is based on a [project on the economics of pandemic preparedness](https://github.com/robj411/p2_drivers).

## References
